\documentclass[11pt]{article}
\usepackage{colacl}
\usepackage{graphicx}
\sloppy



\title{Sudoku Sage: An AI-Powered Interactive Sudoku Assistant}
\author{
  Aidan Gillespie \\
  Vladimir Serov \\
  Drew Phelps
}

\begin{document}
\maketitle


\begin{abstract}
This project proposes an interactive Sudoku platform enhanced with AI-driven assistance. The system allows users to play Sudoku in a clean web-based interface while requesting strategic hints and explanations powered by ChatGPT. The goal is to combine traditional puzzle-solving with personalized real-time guidance that helps players understand optimal moves rather than simply revealing answers. Our implementation integrates a FastAPI backend, a custom front-end board, and an AI reasoning component that interprets the current state of the board to generate helpful suggestions. This approach not only improves the learning experience for new players, but also creates a scalable foundation for premium features such as advanced tutoring, difficulty analysis, and subscription-based puzzle packs. The proposed platform demonstrates the business potential of combining casual gaming with intelligent assistance to increase user engagement and long-term retention.
\end{abstract}

\section{Introduction}
Sudoku remains one of the most widely played logic-based puzzle games, appealing to casual players and enthusiasts alike. While the game is simple in structure, many players struggle to recognize patterns, plan ahead, or identify the next optimal move. Traditional Sudoku apps offer little support beyond basic notes or automatic error checking, leaving users without meaningful guidance on how to improve their reasoning skills. As a result, players often plateau or disengage when puzzles become too difficult.

With the rapid advancement of large language models, there is an opportunity to transform how players interact with puzzles. Sudoku Sage introduces an AI-enhanced Sudoku experience where users can request hints, ask for explanations, or receive strategic advice tailored to the current board state. Instead of merely displaying the solution, the system provides reasoning-based guidance that helps users understand why a move is correct. This creates a more engaging, educational, and personalized puzzle-solving environment.

The goal of this project is to combine a clean, intuitive Sudoku interface with an intelligent assistant capable of interpreting board configurations and generating helpful, context-aware responses. This approach not only improves accessibility for beginners but also lays the foundation for a scalable business model centered around premium tutoring features, difficulty analytics, and interactive puzzle packs. By integrating modern AI technology into a classic game, Sudoku Sage demonstrates how traditional digital experiences can be enhanced to deliver deeper value and increased user engagement.

\section{Literature Review}

\section {System Architecture and Methodology}

\section{Experiments, Tried Approaches, and Abandoned Ideas}

\subsection{Model Experiments}
\subsection{Prompting Experiments}
\subsection{Hint Style Experiments}
\subsection{Reasons for Abandonment}

\section{Implementation Details}

\section{Performance Evaluation}
\subsection{Accuracy Evaluation}
\subsection{User Experience}
\subsection{Cost Evaluation}

\section{Strengths and Weaknesses}

\section{Conclusions}

\section{References}

\bibliographystyle{acl}
\bibliography{sample}

\end{document}
